Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-11 papers/marlowe2019/paper-long.tex
fix david email address
Addesses and emails.
Small fixes and reduce one level in sections 4 and 5

\subsubsection{SBV library}

SBV \cite{SBV} (SMT Base Verification) library provides a high-level API that allows developers to automatically prove properties about Haskell programs, among other functionalities.
The SBV library translates these properties to SMTLib queries, passes them to one or several SMT solvers, and translates the results back to the format in which the queries were written.

\paragraph{\texttt{SBV} monad.}

@@

\paragraph{Limitations}

@@

\subsubsection{Using SBV to analyse Marlowe Contracts}

@@

\paragraph{Custom datatypes}

@@

\subsubsection{Termination proof}

@@

\subsubsection{Valid state and positive account preservation}

@@

\subsubsection{Money preservation and contract timeout}

@@

\paragraph{Money preservation}
Money is not created or destroyed by the semantics. We state this property as follows:

@@

\paragraph{Timeout closes a contract}

@@

\subsubsection{Bound on the maximum number of transactions\label{subsubsec:bound_max_transaction_number}}

>>>>

\subsection{SBV library}

SBV \cite{SBV} (SMT Based Verification) library provides a high-level API that allows developers to automatically prove properties about Haskell programs, among other functionalities.
The SBV library translates these properties to SMTLib queries, passes them to one or several SMT solvers, and translates the results back to the format in which the queries were written.

\subsubsection{\texttt{SBV} monad}

@@

\subsubsection{Limitations}

@@

\subsection{Using SBV to analyse Marlowe Contracts}

@@

\subsubsection{Custom datatypes}

@@

\subsection{Termination proof}

@@

\subsection{Valid state and positive account preservation}

@@

\subsection{Money preservation and contract timeout}

@@

\subsubsection{Money preservation}
Money is not created or destroyed by the semantics. We state this property as follows:

@@

\subsubsection{Timeout closes a contract}

@@

\subsection{Bound on the maximum number of transactions\label{subsubsec:bound_max_transaction_number}}
